Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-03-05 paper/current/main.tex
add_description_on_new_figure_and _update_big_figure

with the hypothesis that a similar fraction of the scholars are mobile in each organization. Then, our gravity model can be written with only terms from mobility data,

@@

\begin{equation}
    \label{eq:sum of the conditional probabiitliy}
    \sum_{j\in\mathpzc{N}_i} p(j|i) = 1
\end{equation}

@@

We can check the evidence that Eq.\ref{eq:real_embedding_relationship} is a good approximation functional form of is $p(i|j)$ in Fig. \ref{fig:real_embedding_relationship}, as high values of flow correspond to high Eq.\ref{eq:real_embedding_relationship} values.

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/use_all_log.pdf}
    \caption{Relationship between the conditional probability $p(j|i)$ \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:real_embedding_relationship}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.png}
	\caption{
		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
		\textbf{a.}
		UMAP projection \autocite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
		Each point corresponds to an organization. 
		Size indicates the size of the organization.
		Color indicates the continent. 
		We re-project subsets of organizational vectors to uncover more complex local structure.
		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking countries South and Central America. 
		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
		Color indicates Census Bureau-designated regions,
		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
		Color indicates sector designation of organization. 
	}
	\label{fig:projection}
\end{figure}

>>>>

with the hypothesis that a similar fraction of the scholars are mobile in each organization. It can be checked in Fig.~\ref{fig:math_part}a. Then, our gravity model can be written with only terms from mobility data,

@@

\begin{equation}
    \label{eq:sum of the conditional probabiitliy}
    \sum_{j \in N} p(j|i) = 1
\end{equation}

@@

We can check the evidence that Eq.\ref{eq:real_embedding_relationship} is a good approximation functional form of is $p(i|j)$ in Fig.~\ref{fig:math_part}b, as high values of flow correspond to high Eq.\ref{eq:real_embedding_relationship} values.

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/use_all_log.pdf}
    \caption{
    \textbf{a}.   Relationship between $M_i$ and $\mu_i$.
    \textbf{b}.   Relationship between the conditional probability $p(j|i)$, Eq. \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:math_part}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.pdf}
	\caption{
		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
		\textbf{a.}
		UMAP projection \autocite{mcinnes2018umap} of the entire embedding space reveals geographic clustering.
		Each point corresponds to an organization. 
		Size indicates the size of the organization.
		Color indicates the continent. 
		We re-project subsets of organizational vectors to uncover more complex local structure.
		\textbf{b.} Re-projection of organizational vectors roughly corresponding to West-Asian, Southeast Asian, and South Asian countries. 
		\textbf{c.} Re-projection of organizations in Spain, Portugal, and the Portuguese- and Spanish-speaking countries South and Central America. 
		\textbf{d.} Re-projection of organizations in the United States reveal geographic clustering based on state.
		Color indicates Census Bureau-designated regions,
		\textbf{e.} Re-projection of organizations in Massachusetts reveal clustering based on organizational sector, prestige. 
		Color indicates sector designation of organization. 
	}
	\label{fig:projection}
\end{figure}
